Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-10 Ben_Manuscripts/structure_paper/Final_Draft.tex
Updated drafts.

  %MRSF: I had a bit of hard time connecting the thesis of this paragraph to the details provided.
  %BJCF: tried reorganizing a bit
  It therefore seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function since contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA of the center of the correlation function 
  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
  behavior with a correlation length that nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.
  %Since all columns in our initial
  %configuration are started at the same $z$-coordinate, $g(z)$ on average exhibits
  %correlation of head groups with other head groups within the same column, with
  %head groups in other columns within the same pore, and with head groups in different pores.

@@

  %BJCF: broke giant paragraph into 3 paragraphs, adjusted theses
  Since the dynamics of this system are slow, and consequently most of our analysis
  has been focused on a set of quenched configurations with some structural 
  characteristics that do not vary significantly with time, we attempted to learn
  more about their time-averaged structures by studying ensembles of shorter 
  simulations started from more independent initial configurations. We created
  ensembles of 40 simulations in both the parallel displaced and sandwiched 
  configurations. We used the same equilibration scheme as above 
  (see Section~\ref{section:equilibration}). However, we built the initial 
  configurations with columns randomly displaced in the $z$-direction and looked at
  the results after 5 ns of unrestrained simulation, which should capture any 
  quenched disorder built in from the initial configurations. We then simulated
  XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
  in Figure~\ref{fig:ensemble_XRD}.

  Qualitatively, the $q_r$ cross-sections of R-$\pi$ generated from ensembles of
  simulations are nearly smooth, with only small spikes near $q_r$=0. These data
  suggest that the average intensity of R-$\pi$ in the ensemble of sandwiched 
  systems is about 3$\times$ higher than that in the ensemble of parallel displaced
  configurations. Compared to our long simulations, the intensity of R-$\pi$
  generated from ensembles of short simulations, decreases by a factor of 3
  and by a factor of 2 for the sandwiched and parallel displaced configurations respectively.

  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
  ensemble shows the best agreement with experiment so far. For simplicity, 
  we will limit the following discussion to the parallel displaced configuration.
  Equivalent data for the sandwiched configuration is presented in Section 
  \ref{S-section:sandwiched_ensemble}.

@@

  %MRSF: is this the clearest thesis?  Similar to each other?  Similar to the amount of disordered viewed in the long simulations? Is the symmetric nature more useful?  I think also this paragraph should be split up more to emphasize findings. 
  %BJCF: thesis changed, added reminder of initial randomization.
  These short independent simulations exhibit a symmetric distribution of quenched
  disorder providing evidence that the quenched disorder is randomized in each system. 
  We remind the reader that the only difference between each independent initial configuration
  is the random $z$-direction displacement that we apply to each column. The
  quenched disorder is then a result of the initial structural collapse that is 
  directed by the randomized velocity vectors of the system's atoms which are drawn from
  a Maxwell-Boltzmann distribution. We pooled the deviations of each head group COM 
  from idealized positions from all independent simulations in order to create the 
  distributions shown in Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
  The distributions appear symmetric meaning that there is an equal chance for a head
  group to displace in the positive or negative $z$, $r$, or $\theta$-direction.

@@

  We observe slow dynamics in our system. Typical diffusion constants for columnar
  liquid crystals have been reported to be between $10^{-11}~ \mathrm{m}^2/\mathrm{s}$ 
  \cite{dong_translational_1984} and $10^{-14}~\mathrm{m}^2/\mathrm{s}$ \cite{dvinskikh_molecular_2002}. 
  %MRSF: see below comment; if not LLC's we should qualify this (electrostatics would likely make slower, since larger
  %energies involved.
  %MRS13: are these hydrophilic/hydrophopic LC?  Ones with electrostatic driving forces are likely 
  % to be even slower.  
  %BJCF: new addtion
  In the case of LLCs, we would expect a diffusion coefficient at the low end of this
  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energy 
  barrier for motion. We measured the diffusion constants of monomers in each of the main 
  systems we studied (see Table \ref{S-table:msd} of the SI) and find they are all on the 
  order of $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers 
  move a full `level' above or below, this may be an overestimate. This slow speed is
  not entirely surprising considering how densely the monomers are packed as implied
  by diffraction experiments. The entangled tails likely restrict both vertical and lateral
  movement.

>>>>

  %MRSF: I had a bit of hard time connecting the thesis of this paragraph to the details provided.
  %BJCF: tried reorganizing a bit
  It therefore seems likely that the discrepancy between the shape and intensity of
  R-$\pi$ generated from our simulations versus experiment is primarily due to
  highly correlated columns in our highly symmetric initial configurations.
  %MRSF2: These next two sentences gets pretty confusing; too many clauses, if, when, since . . . make sentences shorter. 
  If the columns were uncorrelated, $g(z)$ of the ordered sandwiched system 
  would very closely resemble Figure~\ref{fig:z_correlation_sandwich} when we 
  average all $z$-slices of the 3D correlation function since contributions to
  $g(z)$ from head groups in other columns within the same pore, and with head
  groups in different pores would cancel out. However, when we include all 
  $z$-slices in $g(z)$ for our system, rather than restricting it to those 
  $z$-slices within 2.1~\AA of the center of the correlation function 
  (Section~\ref{section:correlation_length}), $g(z)$ shows oscillatory 
  behavior with a correlation length that nearly triples to 12.4 $\pm$ 0.7 \AA.
  (Figure~\ref{fig:z_correlation_fullbox}). The peaks of $g(z)$ are actually 
  reinforced by head groups in neighboring columns which is not expected
  in a system where columns act independently.
  %Since all columns in our initial
  %configuration are started at the same $z$-coordinate, $g(z)$ on average exhibits
  %correlation of head groups with other head groups within the same column, with
  %head groups in other columns within the same pore, and with head groups in different pores.

@@

  %BJCF: broke giant paragraph into 3 paragraphs, adjusted theses
  %MRSF2: broke up the sentence, check to make sure it makes sense.
  Since the dynamics of this system are slow, consequently most of our analysis
  has been focused on a set of quenched configurations with some structural 
  characteristics that do not vary significantly with time.  We therefore attempted to learn
  more about their time-averaged structures by studying ensembles of shorter 
  simulations started from more independent initial configurations. To do this, we created
  ensembles of 40 simulations in both the parallel displaced and sandwiched 
  configurations. We used the same equilibration scheme described in Section~\ref{section:equilibration}. 
  However, we built the initial 
  configurations with columns randomly displaced in the $z$-direction and looked at
  the results after 5 ns of unrestrained simulation, which should capture any 
  quenched disorder built in from the initial configurations. We then simulated
  XRD patterns from the 40 trajectories, concatenated together. The $q_r$ 
  cross-sections of R-$\pi$ generated from the two concatenated trajectories are shown
  in Figure~\ref{fig:ensemble_XRD}.

  Qualitatively, the $q_r$ cross-sections of R-$\pi$ generated from ensembles of
  simulations are nearly smooth, with only small spikes near $q_r$=0. These data
  suggest that the average intensity of R-$\pi$ in the ensemble of sandwiched 
  systems is about 3$\times$ higher than that in the ensemble of parallel displaced
  configurations. Compared to our long simulations, the intensity of R-$\pi$
  generated from ensembles of short simulations decreases by a factor of 3
  and by a factor of 2 for the sandwiched and parallel displaced configurations respectively.

  Overall, the intensity of R-$\pi$ generated from the parallel displaced 
  ensemble of short simulations shows the best agreement with experiment so far. For simplicity, 
  we will limit the following discussion to the parallel displaced configuration.
  Data for the sandwiched configuration is presented in Section 
  \ref{S-section:sandwiched_ensemble}.

@@

  %MRSF: is this the clearest thesis?  Similar to each other?  Similar to the amount of disordered viewed in the long simulations? Is the symmetric nature more useful?  I think also this paragraph should be split up more to emphasize findings. 
  %BJCF: thesis changed, added reminder of initial randomization.
  These short independent simulations exhibit a symmetric distribution of quenched
  disorder providing evidence that the quenched disorder is randomized in each system. 
  The only difference between each independent initial configuration
  is the random $z$-direction displacement that we apply to each column. The
  quenched disorder is then a result of the initial structural collapse that is 
  directed by the randomized velocity vectors of the system's atoms drawn from
  a Maxwell-Boltzmann distribution. We pooled the deviations of each head group COM 
  from idealized positions from all independent simulations in order to create the 
  distributions shown in Figure~\ref{fig:offset_ensemble_pooled} (see Section~\ref{method:simple_systems}).
  The distributions appear symmetric meaning that there is an equal chance for a head
  group to displace in the positive or negative $z$, $r$, or $\theta$-direction.

@@

  We observe slow dynamics in our system. Typical diffusion constants for columnar
  liquid crystals have been reported to be between $10^{-11}~ \mathrm{m}^2/\mathrm{s}$ 
  \cite{dong_translational_1984} and $10^{-14}~\mathrm{m}^2/\mathrm{s}$ \cite{dvinskikh_molecular_2002}. 
  %MRSF: see below comment; if not LLC's we should qualify this (electrostatics would likely make slower, since larger
  %energies involved.
  %MRS13: are these hydrophilic/hydrophopic LC?  Ones with electrostatic driving forces are likely 
  % to be even slower.  
  %BJCF: new addtion
  In the case of LLCs, we would expect a diffusion coefficient at the low end of this
  range since hydrophilic regions of monomers can hydrogen bond, thus increasing the energetic 
  barriers for motion. We measured the diffusion constants of monomers in each of the main 
  systems we studied (see Table \ref{S-table:msd} of the SI) and find they are all on the 
  order of $10^{-14}~\mathrm{m}^2/\mathrm{s}$. However, since on this timescale, no monomers 
  move a full `level' above or below, this may be an overestimate. This slow speed is
  not entirely surprising considering how densely the monomers are packed as implied
  by diffraction experiments. The entangled tails likely restrict both vertical and lateral
  movement.
